---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
set.seed(1014)
```

# emo(ji)

The goal of emo(ji) is to make it very easy to insert emoji into RMarkdown documents.

Emoji data from <https://github.com/muan/emojilib/>.

## Installation

You can install emo from github with:

```R
# install.packages("devtools")
devtools::install_github("hadley/emo")
```

## Example

You can either refer to emoji by their name (which is unique):

```{r}
emo::ji("poop")
```

Or by a keyword. Keywords are not unique so emo::ji will pick one for you at random.

```{r} 
emo::ji("face")
emo::ji("face")
emo::ji("face")
```

You can use keywords with emo::ji_find to find the unique name for an emoji.

```{r}
emo::ji_find("sun")
```

Often you'll use inline like `r '\u60\u60 \u60r emo::ji("smile")\u60 \u60\u60'` `r emo::ji("smile")`

## Keywords

These are all keywords with more than one emoji associated with them.

```{r, echo = FALSE}
keywords <- emo::ji_keyword
keywords <- keywords[lengths(keywords) > 1]

emojis <- purrr::map_chr(keywords, function(x) paste0(emo::ji_name[x], collapse = ""))

cat(paste(names(emojis), ": ", emojis, collapse = "\n"))
```
